Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-08-01 Paper/intro.tex
typos

Today, most such control is exercised at the country level, as
governments have recognized both the threat and the opportunity that
is posed by ubiquitous online communication. For example, much of the
organization, revolutionary momentum, and broadcasting of events
during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and several
countries sought to control these movements by disconnecting
in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing dependence on the Internet and increased
content monitoring, point to the need for improved tools and methods
for studying worldwide Internet structure over time. Previous research has
investigated country level AS topology \cite{DBLP:journals/corr/abs-0903-3218},
focusing on how the global AS graph layout indicates that interdomain routing
for many Internet users depends on the infrastructure of other nations. Here we take
a different approach, presenting a technique to monitor the of paths intercepted
by border ASes, allowing us to compare nations according to how BGP paths enter and exit
each nation.
% Current
% methods have primarily focused on the node level (individual ASes)
% rather than the country level, 
% they have not described how AS topology
% has changed over time with respect to national boundaries, and
% existing BGP simulation methods make it difficult to address 
% questions such as these efficienty and at scale.

>>>>

Today, most such control is exercised at the country level, as
governments have recognized both the threat and the opportunity that
is posed by ubiquitous online communication. For example, much of the
organization, revolutionary momentum, and broadcasting of events
during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and several
countries sought to control these movements by disconnecting
in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing dependence on the Internet and increased
content monitoring, point to the need for improved tools and methods
for studying worldwide Internet structure over time. Previous research has
investigated country level AS topology \cite{DBLP:journals/corr/abs-0903-3218},
focusing on how the global AS graph layout indicates that interdomain routing
for many Internet users depends on the infrastructure of other nations. Here we take
a different approach, presenting a technique to monitor the number of paths intercepted
by border ASes, allowing us to compare nations according to how BGP paths enter and exit
each nation.
% Current
% methods have primarily focused on the node level (individual ASes)
% rather than the country level, 
% they have not described how AS topology
% has changed over time with respect to national boundaries, and
% existing BGP simulation methods make it difficult to address 
% questions such as these efficienty and at scale.
